\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-11-10 draft.tex
revise results statements to match appendix

\noindent When $\tau^a$ is higher, the government agency becomes less likely to renew the antidumping duties, for three reasons. First, the government prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta,\tad)$ indirectly (Lemma~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the government's preferred tariff further (Lemma~\ref{res:bincC}).

@@

\begin{lemma}
  Lobbying effort is weakly decreasing in the antidumping duties. \hyperlink{Pr_tad_indir}{Proof}
  \label{res:tad_indir}
\end{lemma}

\begin{result}
	The total probability that the antidumping duties will be renewed is decreasing in level of the antidumping duties $\tad$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial \tad} \leq 0$). \hyperlink{Pr_tad_total}{Proof}
	\label{res:tad_total}
\end{result}

@@

\begin{lemma}
  Lobbying effort is weakly increasing in the uniform exogenous positive shifts of the political weighting function. \hyperlink{Pr_ga_indir}{Proof}
  \label{res:ga_indir}
\end{lemma}

\begin{result}
	The total probability that the antidumping duties will be renewed is increasing in $\ga$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \ga(\cdot)} \geq 0$). \hyperlink{Pr_ga_total}{Proof}
	\label{res:ga_total}
\end{result}

@@

Then $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)} = - \frac{\partial}{\partial e} \left( f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)} \right) = 
	   - f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial \ga(\cdot) \partial e} - \frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)} \frac{\partial f_\ta}{\partial e} = - f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial \ga(\cdot) \partial e} $
where the above equality holds because the pdf of $\ta$ does not depend on $e$. When $\ga(\cdot)$ shifts up, $\frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)}$ becomes less negative, so $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)} \leq 0$.

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_ga_total}{Proof of Result~\ref{res:ga_total}}}: \\
$\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \ga(\cdot)} + \frac{\partial r}{\partial \ga(\cdot)}$. $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}. $\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}. $\frac{\partial r}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_dir}. Thus the entire expression is non-negative. $\hfill\blacksquare$

>>>>

\noindent When $\tau^a$ is higher, the government agency becomes less likely to renew the antidumping duties, for three reasons. First, the government prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying (Lemma~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the government's preferred tariff further (Lemma~\ref{res:bincC}).

@@

\begin{lemma}
  Higher antidumping duties may lead to either an increase or decrease in lobbying effort. \hyperlink{Pr_tad_indir}{Proof}
  \label{res:tad_indir}
\end{lemma}

\begin{result}
	The total probability that the antidumping duties will be renewed is most likely to decrease in level of the antidumping duties but it can increase in the antidumping duties if the indirect effect is positive and large enough to outweigh the direct effect. \hyperlink{Pr_tad_total}{Proof}
	\label{res:tad_total}
\end{result}

@@

\begin{lemma}
  Lobbying effort is weakly decreasing in exogenous positive shifts of the political weighting function. \hyperlink{Pr_ga_indir}{Proof}
  \label{res:ga_indir}
\end{lemma}

\begin{result}
	The total probability that the antidumping duties will be renewed is increasing in $\ga(\cdot)$ if the direct effect dominates and is decreasing in $\ga(\cdot)$ if the indirected effect dominates. \hyperlink{Pr_ga_total}{Proof}
	\label{res:ga_total}
\end{result}

@@

Then $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)} = - \frac{\partial}{\partial e} \left( f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)} \right) = 
	   - f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial \ga(\cdot) \partial e} - \frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)} \frac{\partial f_\ta}{\partial e} = - f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial \ga(\cdot) \partial e} $
where the above equality holds because the pdf of $\ta$ does not depend on $e$. When $\ga(\cdot)$ shifts up, $\frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)}$ becomes less negative, so $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)} \leq 0$. Thus $\frac{\partial e}{\partial \ga(\cdot)} \leq 0$.

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_ga_total}{Proof of Result~\ref{res:ga_total}}}: \\
$\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \ga(\cdot)} + \frac{\partial r}{\partial \ga(\cdot)}$. $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}. $\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}. $\frac{\partial r}{\partial \ga(\cdot)}$ is non-positive by Lemma~\ref{res:ga_dir}. Thus the sign of $\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)}$ can be positive, zero or negative. $\hfill\blacksquare$
